The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-12 Paper_third_version/Article_UV_Mexico.tex
Delete unused references

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
meters above sea level (m asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. Calibration of the
UV sensors has been carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
network’s sensors have been compared for at least one week against the UV
readings from the reference sensor to derive new calibration factors, which typically differed
from the old ones by 2\% or less.
Reference sensors have been also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
Long term calibration drifts are minimized by these yearly re-calibrations.
Although at the beginning only a few stations were in operation and
varied, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where the UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~in each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{June-July}                              & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}
      }TUV pristine atmosphere \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.05, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{Comparison of June-July UVI maxima measured directly (SIMAT), inferred from satellite-based
        observations (OMI), and modeled for different pollution levels (TUV).
      }}
  \label{table:TUVmodel}
\end{table}

@@

Two decades of observations in Mexico City demonstrate unequivocally
that air pollution reduces UV radiation at the ground. The ground-based
observations are well below values derived from satellite-based
observations. Although ideally both data sets should match,
space-based observations have difficulting inferring the extent of UV absorption by urban gases and particles.
Thus, they do not reveal long-term UVI trends, due to substantial air quality improvemnets, that are evident in the ground-based UVI data.
When typical values of pollutant: aerosols,
tropospheric ozone, NO\textsubscript{2}
and SO\textsubscript{2}, are included in a model (e.g. TUV), the
differences between satellite-derived and ground-based measured values
are explained and can be attributed quantitatively to individual
observed pollutants. Long term improvements in air quality over the last two decades,
were accompanied by statistically significant increases in the
observed UVI, in agreement with the model-predicted changes.

>>>>

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
meters above sea level (m asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. Calibration of the
UV sensors has been carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
network’s sensors have been compared for at least one week against the UV
readings from the reference sensor to derive new calibration factors, which typically differed
from the old ones by 2\% or less.
Reference sensors were also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
Long term calibration drifts are minimized by these yearly re-calibrations.
Although at the beginning only a few stations were in operation and
varied, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where the UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~in each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{June-July}                              & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}
      }TUV pristine atmosphere \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{Comparison of June-July UVI maxima measured directly (SIMAT), inferred from satellite-based
        observations (OMI), and modeled for different pollution levels (TUV).
      }}
  \label{table:TUVmodel}
\end{table}

@@

Two decades of observations in Mexico City demonstrate unequivocally
that air pollution reduces UV radiation at the ground. The ground-based
observations are well below values derived from satellite-based
observations. Although ideally both data sets should match,
the satellite has a limitation to seeing boundary layer absorbers.
Thus, they do not reveal long-term UVI trends, due to substantial air quality improvemnets, that are evident in the ground-based UVI data.
When typical values of pollutant: aerosols,
tropospheric ozone, NO\textsubscript{2}
and SO\textsubscript{2}, are included in a model (e.g. TUV), the
differences between satellite-derived and ground-based measured values
are explained and can be attributed quantitatively to individual
observed pollutants. Long term improvements in air quality over the last two decades,
were accompanied by statistically significant increases in the
observed UVI, in agreement with the model-predicted changes.
